\bf Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-02-08 main.Rmd
title change

---
title: Exploring probability distributions for bivariate temporal granularities
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

keywords:
- data visualization
- statistical distributions
- time granularities
- periodicties
- grammar of graphics
- R

>>>>

---
title: Visualizing probability distributions across bivariate cyclic temporal granularities

# to produce blinded version set to 1
blinded: 0

authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

keywords:
- data visualization
- statistical distributions
- time granularities
- calendar algebra
- periodicties
- grammar of graphics
- R

### 2020-02-08 main.tex
title change

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{}

@@

\if0\blind
{
  \title{\bf Exploring probability distributions for bivariate temporal granularities}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Exploring probability distributions for bivariate temporal granularities}
  \end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} data visualization, statistical distributions, time granularities, periodicties, grammar of graphics, R
\vfill

>>>>

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

\if0\blind
{
  \title{\bf Visualizing probability distributions across bivariate cyclic temporal granularities}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visualizing probability distributions across bivariate cyclic temporal granularities}
  \end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} data visualization, statistical distributions, time granularities, calendar algebra, periodicties, grammar of graphics, R
\vfill
